---
title: "Data Analysis Template"
output: 
  html_document: 
    fig_height: 4
    highlight: pygments
    theme: spacelab
---

## Import Packages and Libraries

```{r load-packages, message = FALSE}
library(ggplot2)
library(dplyr)
library(statsr)
library(tidyr)
library(rmarkdown)
```


* * *

## (P)ACE - Plan Phase
### Part 1 - Data
#### How were the observations in the dataset collected?



* * *

### Part 2 - Research Question
#### Project Scope



* * *
## P(A)CE - Analyze Phase
### Part 3 - EDA (Exploratory Data Analysis)
#### Investigate the Dataset

```{r eda_1}

```

##### Descriptive Statistics
```{r eda_2}

```

##### Pairplot to visualize relationships between pairs of variables
```{r eda_3}

```

#### Data Manipulation and Cleaning
```{r eda_4}

```


##### Initial Insights
```{r eda_5}

```

#### Check Statistical Test Conditions/Assumptions (If Applicable)
```{r eda_6}

```

* * *

## PA(C)E - Construct Phase of the PACE Framework
### Part 4 - Modeling/Inference 

H0 (nothing going on):
HA (something going on):

#### Create a Hold-Out Sample (If Applicable)
```{r modeling_inference_1}

```


#### Build and Fit The Model (If Applicable)
```{r modeling_inference_2}

```

#### Run Statistical Tests (If Applicable)
```{r modeling_inference_3}

```

#### Check Model Conditions/Assumptions Post Model Construction (If Applicable)

```{r modeling_inference_4}

```

##### Linearity

```{r modeling_inference_5}

```

##### Independent Observations

```{r modeling_inference_6}

```

##### Normality

```{r modeling_inference_6}

```

##### Homoscedasticity

```{r modeling_inference_7}

```

##### No Multicollinearity (If Applicable)

```{r modeling_inference_8}

```

* * *

### Part 5 - Prediction/Conclusion
```{r modeling_inference_9}

```

## PAC(E)- Execute Phase of the PACE Framework
### What Story does the Data Tell?

